Predicting the Capture Rate of Pokemon

### 2022-11-25 Draft2.Rmd
sad times

```{r}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
library(kknn)
library(janitor)
# Assigning the data to a variable
pokemon <- read_csv("data/pokemon.csv")
tidymodels_prefer()
set.seed(0124)
```

@@

>>>>

```{r}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
library(kknn)
library(janitor)
library(ISLR)
library(discrim)
library(poissonreg)
library(glmnet)
library(corrr)
library(corrplot)
library(randomForest)
library(xgboost)
library(rpart.plot)
library(vip)
library(ranger)
# Assigning the data to a variable
pokemon <- read_csv("data/pokemon.csv")
tidymodels_prefer()
set.seed(0124)
```

@@

```{r}
# Setting up random forest model with specified tuning parameters and engine
rf_spec <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) %>% 
  set_engine("ranger", importance = "impurity") %>% 
  set_mode("regression")

# Setting up random forest workflow
rf_workflow <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(rf_spec)

# Creating a regular grid with 8 levels each
rf_parameter_grid <- grid_regular(mtry(range = c(1, 19)), trees(range = c(200,1000)), min_n(range = c(5,20)), levels = 8)
```

```{r, eval = FALSE}
# Tuning the model with roc_auc as a metric
rf_tune_res <- tune_grid(
  rf_workflow,
  resamples = pokemon_folds,
  grid = rf_parameter_grid
)

# Saving the fit
write_rds(rf_tune_res, file = "rf.rds")
```

```{r}
# Loading in the random forest
rf_tuned <- read_rds(file = "rf.rds")

# Producing autoplot of results
autoplot(rf_tuned)
```

```{r}
# Finding roc_auc of best performing random forest model on folds
rf_best_roc_auc <- rf_tuned %>% 
  collect_metrics() %>% 
  arrange(desc(mean)) %>% 
  head(1)

rf_best_roc_auc
```

```{r}
best_rf <- select_best(rf_tuned)
rf_final_workflow <- finalize_workflow(rf_workflow, best_rf)
rf_final_fit <- fit(rf_final_workflow, data = pokemon_train)

rf_final_fit %>% 
  extract_fit_engine() %>% 
  vip()
```

### BOOSTED TREE
```{r}
# Setting up boosted tree model
boosted_spec <- boost_tree(trees = tune()) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

# Setting up boosted trees workflow
boosted_workflow <- workflow() %>% 
  add_recipe(pokemon_recipe) %>% 
  add_model(boosted_spec)

# Creating regular grid
boosted_grid <- grid_regular(trees(range = c(10, 2000)), levels = 10)
```

```{r, eval = FALSE}
# Tuning and specifying roc_auc
boosted_tune_res <- tune_grid(
  boosted_workflow,
  resamples = pokemon_folds,
  grid = boosted_grid
)

# Saving the fit
write_rds(boosted_tune_res, file = "boosted.rds")
```

```{r}
# Loading the fit
boosted_tuned <- read_rds(file = "boosted.rds")

# Printing autoplot of results
autoplot(boosted_tuned)
```

```{r}
# Finding roc_auc of best performing boosted tree model on folds
boosted_best_roc_auc <- boosted_tuned %>% 
  collect_metrics() %>% 
  arrange(desc(mean)) %>% 
  head(1)

boosted_best_roc_auc
```
